If the Null Fits, You Must Omit: Ubiquitous False Detections of Group Polarization

### 2025-08-12 GroupPolarizationStatmod/paper/ms.tex
fuller explanation of code in README, started in Methods with new data-model flow fig

>>>>

\begin{figure}
  \centering
    \includegraphics[width=0.8\textwidth]{Figures/Model/data-model-flow.png}
  \caption{\textbf{Workflow of the GP-stats simulation and analysis pipeline
  for estimating false detection rates under null-consistent conditions.} Colored boxes indicate file types: teal = R scripts, blue = data files, orange = plotting scripts, cyan = Slurm batch script. Arrows show the flow from parameter estimation (hillclimbing or Shiny app) to Bayesian null model fitting on the cluster, aggregation of simulated results, and final visualization.}
  \label{fig:}
\end{figure}
